### 2024-08-17 paper.tex
remark about required type of quotient
m

\begin{lemma}
    \(V = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} V_{w,r}\).
    Further, \(V_{w_1r_1} = V_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \(\lambda_{w_1} = \lambda_{w_2} \land r_1 = r_2\).
    When \(V_{w_1r_1} \neq V_{w_2r_2}\), we have \(V_{w_1r_1} \cap V_{w_2r_2} = \emptyset\).
\end{lemma}
\begin{proof}
    TODO
\end{proof}
Now, fix any \(w\) and \(r\).
We will find the irreducible components of \(V_{w,r}\).
These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(V\) will be the irreducible components of \(V\).
\par Let 
\[G := \{P \in \GL_m : P^{-1} X P = X\},\]
and
\[G_{wr} := \{P \in \GL_m : \forall b. \exists b'. (P^{-1}, I_n) A_{e_{wr}, b} (P, I_n) = A_{e_{wr}, b'}\}.\]
If you write out the condition \(A_{e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\) as a matrix equation, it is plain to see that 
\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
\par Now, define 
\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
Let \(G\) act on \(V_{wr}\) by
\[P \cdot (A_{e_{wr},b}, U) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)U) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) U).\]
\par Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\) defined by
\[(x, P) \mapsto P \cdot x.\]
By restriction of \(G\) to \(G_{wr}\) and \(V_{wr}\) to \(U_{wr}\), we obtain an action of \(G_{wr}\) on \(U_{wr}\).
Then, letting \(G_{wr}\) act on \(G\) by left multiplication, we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
\begin{lemma}
    As an algebraic variety, \(G\) is irreducible.
\end{lemma}
\begin{proof}
    not sure why at the moment
\end{proof}
\begin{lemma}
    % The map \(\varphi\) is a geometric quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
    The map \(\varphi\) is some sort of quotient by the action of \(G_{wr}\).
    % The map \(X \mapsto \overline{\varphi(X \times G)}\) is a bijection from the irreducible components of \(U_{wr}\) to the irreducible components of \(V_{wr}\).
\end{lemma}
\begin{proof}
    What kind?
    % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
    % Let \(X_1, ..., X_k\) be the irreducible components of \(U_{wr}\).
    % It is clear that \(V_{mr} = \bigcup_i \overline{\varphi(X_i \times G)}\).
    % And if we take \(x \in X_i \setminus \bigcup_{j \neq i} X_j\), it is clear (since \(G\) acts faithfully on itself) that \(\varphi(x, I_m)\)
    % All that remains is to show that \(X_i \notin \bigcup_{j \neq i} \overline{\varphi(X_i \times G)}\).
    % Indeed, 
\end{proof}
Our strategy is to find the irreducible components \(X \subseteq U_{wr}\), and we will then argue that the irreducible components of \(V_{wr}\) are of the form \(\varphi(X \times G)\).
So, we will now find the irreducible components of \(U_{wr}\).

>>>>

\begin{lemma}
    \(V = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} V_{w,r}\).
    Further, \(V_{w_1r_1} = V_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \(\lambda_{w_1} = \lambda_{w_2} \land r_1 = r_2\).
    When \(V_{w_1r_1} \neq V_{w_2r_2}\), we have \(V_{w_1r_1} \cap V_{w_2r_2} = \emptyset\).
\end{lemma}
\begin{proof}
    TODO
Now, fix any \(w\) and \(r\).
We will find the irreducible components of \(V_{w,r}\).
These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(V\) will be the irreducible components of \(V\).
\par Let 
\[G := \{P \in \GL_m : P^{-1} X P = X\},\]
and
\[G_{wr} := \{P \in \GL_m : \forall b. \exists b'. (P^{-1}, I_n) A_{e_{wr}, b} (P, I_n) = A_{e_{wr}, b'}\}.\]
If you write out the condition \(A_{e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\) as a matrix equation, it is plain to see that 
\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
\par Now, define 
\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
Let \(G\) act on \(V_{wr}\) by
\[P \cdot (A_{e_{wr},b}, U) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)U) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) U).\]
\par Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\) defined by
\[(x, P) \mapsto P \cdot x.\]
By restriction of \(G\) to \(G_{wr}\) and \(V_{wr}\) to \(U_{wr}\), we obtain an action of \(G_{wr}\) on \(U_{wr}\).
Then, letting \(G_{wr}\) act on \(G\) by left multiplication, we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
\begin{lemma}
    As an algebraic variety, \(G\) is irreducible.
\end{lemma}
\begin{proof}
    not sure why at the moment
\begin{lemma}
    % The map \(\varphi\) is a geometric quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
    The map \(\varphi\) is some sort of quotient by the action of \(G_{wr}\).
    % The map \(X \mapsto \overline{\varphi(X \times G)}\) is a bijection from the irreducible components of \(U_{wr}\) to the irreducible components of \(V_{wr}\).
\end{lemma}
\begin{proof}
    What kind?
    All I need is something that allows me to deduce the dimension of the quotient!
    % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
    % Let \(X_1, ..., X_k\) be the irreducible components of \(U_{wr}\).
    % It is clear that \(V_{mr} = \bigcup_i \overline{\varphi(X_i \times G)}\).
    % And if we take \(x \in X_i \setminus \bigcup_{j \neq i} X_j\), it is clear (since \(G\) acts faithfully on itself) that \(\varphi(x, I_m)\)
    % All that remains is to show that \(X_i \notin \bigcup_{j \neq i} \overline{\varphi(X_i \times G)}\).
    % Indeed, 
Our strategy is to find the irreducible components \(X \subseteq U_{wr}\), and we will then argue that the irreducible components of \(V_{wr}\) are of the form \(\varphi(X \times G)\).
So, we will now find the irreducible components of \(U_{wr}\).
\par To do this, we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
\begin{theorem}
    (Needs citation!)
    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
\end{theorem}
Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
